From Water Dynamics to Rainfed Landscapes with GRASS GIS\bigskip

### 2014-04-16 grassposter/2014_EGU_WD_Landscape/poster.tex
Updated poster
git-svn-id: https://svn.osgeo.org/grass/grass-promo@59745 15284696-431f-4ddb-bdfa-cd5b030d7da7

}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Biotic Zoning}{
\smallskip
Object based classification (\textit{i.segment}) of the sum transpiration for each year has been done and merged, resulting areas were clumped (\textit{r.clump}) and averaged statistics of yearly transpiration extracted (\textit{r.stats.zonal}).\newline
\begin{center}
	\includegraphics[width=0.45\textwidth]{./images/seg_ta_years_clump_reclass_ta_avg}
\end{center}
This perspective proposes that irrigated areas along the Mekong may not be transpiring as much as the recession cropping areas around Tonle Sap. Whether the transpiration in recession zones is actually used by crops all the time depends on the opportunity of farming intensification and risk avoidance.\newline
}

>>>>

}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\blocknode{Biotic Zoning}{
\smallskip
Object based classification (\textit{i.segment}) of the sum transpiration for each year has been done and merged, resulting areas were clumped (\textit{r.clump}) and averaged statistics of yearly transpiration extracted (\textit{r.stats.zonal}).\newline
Rainfed cropping in Isarn (Part 1) is clearly identified as low transpiration signal (red colour), Recession cropping areas around Tonle Sap (Part 2 \& 3) are high signals (Blue and green) with both noise and a negative impact on transpiration in Part 2 around mid-year (Green signal drop). A southern area (Part 4) of most probably rainfed benefiting from flood to some extent to propose some kind of recession cropping with a mid-year transpiration raise signal (Violet).\newline
\begin{center}
	\begin{tabular}{cc}
 	\begin{tabular}{p{0.5\textwidth}}
 	\includegraphics[width=0.45\textwidth]{./images/seg_ta_years_clump_reclass_ta_avg}\\
 	\vspace{5mm}
 	This perspective proposes that irrigated areas along the Mekong may not be transpiring as much as the recession cropping areas around Tonle Sap. Whether the transpiration in recession zones is actually used by crops all the time depends on the opportunity of farming intensification and risk avoidance.\newline 
	\end{tabular}
 	& 
 	\begin{tabular}{c}
 	\includegraphics[width=0.45\textwidth]{./images/Ta_loc}\\
 	\includegraphics[width=0.45\textwidth]{./images/Ta}
	\end{tabular}
	\end{tabular}
\end{center}
}
